---
title: "milestone4"
format: html
editor: visual
---

```{r setup, include=FALSE}

```

## Packages 
```{r}
pacman::p_load(tidyverse)
```


## Steps to configureing GitHub 

### Set up 

git config --global user.name "username"

git config --global user.email "email"



### connect to repository 

git remote add 



## Assignment Details

Please prepare a document containing the 4 pieces of information requested below, in the order listed. This does not have to be fancy or attractively formatted! There's no page limit or expectation. Screenshots of R output are perfectly acceptable. All plots should have titles and axis labels that are easy to interpret.

### Objective 1

For the two categorical variables (choose two for this milestone if you have more than two), provide box plots of the relationships with the exposure variable using the log-transformed values.

### Objective 2
For the two categorical variables, provide the results of ANOVA against the log-transformed exposure variable. If there is a significant association, provide the results of a Tukey HSD test.

### Objective 3
For the two categorical variables, provide the results of a linear regression model using the log-transformed values, including the estimated risk ratios for each variable category and their confidence intervals.

### Objective 4
Using information from 1-3, write a short interpretation (\<100 words) of your findings for each variable. Again, this can be done in bullet form for the milestone. Do not simply repeat the results reported in 1-3; use your knowledge and experience to describe their meaning.

```{r}

df.no2 = 
  read_csv("../Data/no2_lme.csv") 

df.no2$no2.mle <- round(df.no2$no2.mle, 2)


```
